The Anatomy of a Temporal Summarization System

### 2015-01-24 motivation.tex
updated intro and motivation. Both complete

At times of crisis, however, social media can overwhelm current information
systems with the quantity of information, much of which is irrelevant,
unnecessary detail, or out of date. Many approaches have focused on

@@

Most multi-document summarization approaches involve either sentence 
clustering or ranking or both to select summary sentences.
When the summarization task
is broad or underspecified, clustering is most appropriate in that the data
``speaks for itself.'' This is probably most true when summarization is 
interpreted to mean exploratory data analysis. 
When there are more constraints on the output, as in many text summarization
tasks,
it is often easier to design appropriate features for the ranking approach, 
either by rule or learning-to-rank. The primary contribution of this paper
is a framework for combining both of these approaches using affinity
propagation clustering. Additionally, we provide a task specific evaluation
of this clustering model on the TREC Temporal Summarization task.

>>>>

At times of crisis, however, social media can overwhelm current information
systems with the quantity of information, much of which is irrelevant,
unnecessary detail, or out of date. Many approaches have focused on
human-in-the-loop approaches \cite{?} to enable people on the ground to update
crisis interfaces with information about needs. Others have ..
%KM - Chris - fill this out a bit.

@@

Multi-document summarization offers potential for enabling automatic updates of
relevant, salient information at regular intervals. It would provide
information even when human volunteers are unable to and would filter out
unnecessary and irrelevant detail. 
Most generic multi-document summarization approaches involve either sentence 
clustering or ranking sentences according to metrics that measure the salience
of their words. 
When the summarization task
is broad or underspecified,
%clustering is most appropriate in that the data
these methods are appropriate as they let the data
``to speak for itself.''
%This is probably most true when summarization is 
%interpreted to mean exploratory data analysis. 
When there are more constraints on the output, as in query-focused
summarization or the crisis update task we present here,
results are more accurate when
%often easier to design
appropriate features for the ranking approach are used (e.g., amount of word
overlap for the query-focused approach).
%either by rule or learning-to-rank.
The primary contribution of this paper
is a framework for combining both of these approaches using affinity
propagation clustering as well as disaster-specific features.
